Process-based phenotypes: an application to the ontology of cell physiology

### 2011-11-25 trunk/paper/drinking.tex

\subsection{Processes, their participants and qualities}
Processes are entities that are temporally extended: processes have
temporal parts and {\em unfold} through time. Examples of classes that
may have processes as instances include {\em Drinking}, {\em
  Triathlon} or {\em Apoptosis}.

>>>>

\subsection{Processes, their participants and qualities}
\begin{figure}
  \centering
  \includegraphics[width=.45\textwidth]{onto.pdf}
  \caption{Overview over ...\label{fig:onto}}
\end{figure}

Most biomedical ontologies share common distinctions between different
kinds of entities: physical objects, qualities, functions and
processes. A physical object is an entity that is present as a whole
at a time point, i.e., an entity that has no temporal parts. A quality
is an attribute or feature of an entity. Physical objects together
with their qualities give rise to functions, which are capabilities or
potentials of physical objects. These functions can then be realized
by processes, which are temporally extended entities. Examples of
classes that may have processes as instances include {\em Drinking},
{\em Triathlon} or {\em Apoptosis}.  Figure \ref{fig:onto} illustrates
these basic categories of being.
